---
title: "Ejercicios varios 3"
author: "Jeshua Zyanya Bejarano García"
date: "2024-05-30"
output: html_document
---
## R for Data Science, Data visualization, Section 1.5: Visualizing relationship.

Calling libraries.
```{r}
library("tidyverse")
penguins_df <- palmerpenguins::penguins
```

1. Which variables in mpg are categorical? Which variables are numerical?
```{r}
glimpse(mpg)
?mpg
```
The categorical variables are trans, drv, fl, class.
The numerical variables are displ, cyl, cty, hwy.

2. Make a scatterplot of hwy vs. displ using the mpg data frame. Next, map a third, numerical variable to color, then size, then both color and size, then shape. How do these aesthetics behave differently for categorical vs. numerical variables?
```{r}
ggplot(data=mpg,mapping=aes(x=displ,y=hwy)) +
  geom_point()
```
```{r}
ggplot(data=mpg,mapping=aes(x=displ,y=hwy)) +
  geom_point(mapping=aes(color=cyl))
```
```{r}
ggplot(data=mpg,mapping=aes(x=displ,y=hwy)) +
  geom_point(mapping=aes(x=displ,y=hwy,size=cyl))
```
```{r}
ggplot(data=mpg,mapping=aes(x=displ,y=hwy)) +
  geom_point(mapping=aes(color=cyl,size=cty))
```
3. In the scatterplot of hwy vs. displ, what happens if you map a third variable to linewidth?
```{r}
ggplot(data=mpg,mapping=aes(x=displ, y=hwy, linewidth=cyl)) +
  geom_point()
```
5. Make a scatterplot of bill_depth_mm vs. bill_length_mm and color the points by species. What does adding coloring by species reveal about the relationship between these two variables? What about faceting by species?
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_length_mm, y=bill_depth_mm, color=species))+
  geom_point()
```
We can note that for an island, a clear fit of the bill length and depth.
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_length_mm, y=bill_depth_mm)) +
  geom_point() +
  facet_wrap(~species)
```
6. Why does the following yield two separate legends? How would you fix it to combine the two legends?
```{r}
ggplot(
  data = penguins_df,
  mapping = aes(
    x = bill_length_mm, y = bill_depth_mm, 
    color = species, shape = species
  )
) +
  geom_point() +
  labs(color = "Species")
```
Our change
```{r}
ggplot(
  data = penguins_df,
  mapping = aes(
    x = bill_length_mm, y = bill_depth_mm, 
    color = species, shape = species
  )
) +
  geom_point() +
  labs(color = "Species",shape="Species")
```
7. Create the two following stacked bar plots. Which question can you answer with the first one? Which question can you answer with the second one?
```{r}
ggplot(penguins_df, aes(x = island, fill = species)) +
  geom_bar(position = "fill")
ggplot(penguins_df, aes(x = species, fill = island)) +
  geom_bar(position = "fill")
```

Exercises 1.6.1
1. Run the following lines of code. Which of the two plots is saved as mpg-plot.png? Why?
```{r}
ggplot(mpg, aes(x = class)) +
  geom_bar()
ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave("mpg-plot.png")
```
