---
title: "Ejercicios varios ggplot 2"
author: "Jeshua Zyanya Bejarano García"
date: "2024-05-30"
output: html_document
---
## R for Data Science, Data visualization, Section 1.4: Visualizing distributions.

Calling libraries.
```{r}
library("tidyverse")
penguins_df <- palmerpenguins::penguins
```

1. Make a bar plot of species of penguins, where you assign species to the y aesthetic. How is this plot different?
```{r}
ggplot(data = penguins_df, mapping=aes(y = fct_infreq(species))) +
  geom_bar()
```

2. How are the following two plots different? Which aesthetic, color or fill, is more useful for changing the color of bars?
```{r}
ggplot(penguins_df, aes(x = species)) +
  geom_bar(color = "red")

ggplot(penguins_df, aes(x = species)) +
  geom_bar(fill = "red")
```
3. What does the bins argument in geom_histogram() do?

R. They divide the variable in equal parts to graph the histogram.

4. Make a histogram of the carat variable in the diamonds dataset that is available when you load the tidyverse package. Experiment with different binwidths. What binwidth reveals the most interesting patterns?
```{r}
ggplot(data = diamonds, mapping=aes(x=carat))+
  geom_histogram(binwidth=0.01)
```
