---
title: "Ejercicios varios ggplot"
author: "Jeshua Zyanya Bejarano García"
date: "30/05/2024"
output: html_document
---
## R for Data Science, Data visualization, Section 1.2: ggplot calls.

Calling libraries.
```{r}
library("tidyverse")
```

1. How many rows are in penguins? How many columns?
```{r}
penguins_df <- palmerpenguins::penguins
glimpse(penguins_df)
```
There are 344 rows in penguins dataframe.

2. What does the bill_depth_mm variable in the penguins data frame describe? Read the help for ?penguins to find out.
```{r}
?palmerpenguins::penguins
```
bill_depth_mm indicates the bill depth in milimeters.

3. Make a scatterplot of bill_depth_mm vs. bill_length_mm. That is, make a scatterplot with bill_depth_mm on the y-axis and bill_length_mm on the x-axis. Describe the relationship between these two variables.
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_length_mm, y=bill_depth_mm)) + 
  geom_point()
```

It seems like there are not relashionship between both variables.

4. What happens if you make a scatterplot of species vs. bill_depth_mm? What might be a better choice of geom?
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_depth_mm, y=species)) + 
  geom_point()
```
We thinka boxplot is a better choice of graph.
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_depth_mm, y=species)) + 
  geom_boxplot()
```

5. Why does the following give an error and how would you fix it?
```{r}
ggplot(data = penguins_df) + 
  geom_point()
```
The error arise because no axis have written. We need to put two variables as the new axis.

6. What does the na.rm argument do in geom_point()? What is the default value of the argument? Create a scatterplot where you successfully use this argument set to TRUE.
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_length_mm, y=bill_depth_mm)) + 
  geom_point(na.rm = T)
```
na.rm remove silently the existing NA's.

7. Add the following caption to the plot you made in the previous exercise: “Data come from the palmerpenguins package.” Hint: Take a look at the documentation for labs().
```{r}
ggplot(data=penguins_df, mapping=aes(x=bill_length_mm, y=bill_depth_mm)) + 
  geom_point(na.rm = T) + 
  labs(caption="Data come from the palmerpenguins package.")
```

8. Recreate the following visualization. What aesthetic should bill_depth_mm be mapped to? And should it be mapped at the global level or at the geom level?
```{r}
ggplot(
  data = penguins_df,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point(na.rm=T, mapping = aes(color = bill_depth_mm)) +
  geom_smooth(method = "loess")
```
Note is important colorying in geom_point for a unified smoothing.

9. Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.
```{r}
ggplot(
  data = penguins_df,
  mapping = aes(x = flipper_length_mm, y = body_mass_g, color = island)
) +
  geom_point() +
  geom_smooth(se = FALSE)
```

10. Will these two graphs look different? Why/why not?
```{r}
ggplot(
  data = penguins_df,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point() +
  geom_smooth()

ggplot() +
  geom_point(
    data = penguins_df,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  ) +
  geom_smooth(
    data = penguins_df,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  )
```